\vspace{\baselineskip} The population of long-period transiting exoplanets \vspace{-2.5\baselineskip}

### 2016-07-20 document/ms.tex
adding some refs

\title{%
The population of long-period transiting exoplanets
\vspace{-3\baselineskip}  % OMG AASTEX6 IS SO BROKEN
}

@@

\author{%
    Daniel~Foreman-Mackey\altaffilmark{1,\uw},
    Timothy~D.~Morton\altaffilmark{\princeton},
    David~W.~Hogg\altaffilmark{\scda,\nyu,\mpia,\cds},
    Eric~Agol\altaffilmark{\uw}, and
    Bernhard~Sch\"olkopf\altaffilmark{\mpis}
}

@@

\section{Introduction}

@@

Relaxing the requirement of three transits requires a higher signal-to-noise
threshold per transit for validating candidate planets that display only one
to two transits.
Higher signal-to-noise allows matching the candidate transit to the expected
shape of a limb-darkened light curve, as well as ruling out various false
alarms.  This is analagous to microlensing surveys, for which a planet can only be
detected once, thus requiring high signal-to-noise for a reliable detection
\citep{Gould:2004}.  %http://arxiv.org/abs/astro-ph/0405217

>>>>

\title{%
\vspace{\baselineskip}
The population of long-period transiting exoplanets
\vspace{-2.5\baselineskip}  % OMG AASTEX6 IS SO BROKEN
}

@@

\author{%
    Daniel~Foreman-Mackey\altaffilmark{1,\uw},
    Timothy~D.~Morton\altaffilmark{\princeton},
    David~W.~Hogg\altaffilmark{\scda,\nyu,\mpia,\cds},
    Eric~Agol\altaffilmark{\uw}, and
    Bernhard~Sch\"olkopf\altaffilmark{\mpis}
    \vspace{\baselineskip}
}

@@

\clearpage
\section{Introduction}

@@

Relaxing the requirement of three transits requires a higher signal-to-noise
threshold per transit for validating candidate planets that display only one
to two transits.
Higher signal-to-noise allows matching the candidate transit to the expected
shape of a limb-darkened light curve, as well as ruling out various false
alarms.  This is analagous to microlensing surveys, for which a planet can only be
detected once, thus requiring high signal-to-noise for a reliable detection
\citep{Gould:2004}.
